SaPaFigures

### 2022-02-23 R/PaperFigures.Rmd
gbg

```{r setup, include=FALSE}
library(pixmap)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library(stringr)

@@

```
#####

@@

PlotInCFUs2<- function(){
  ggplot()+
    geom_jitter(data = CFUInOutPostWt,aes(x=Species,y=PercentIn, color = Condition),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent), ymax = (meanInPercent), group = Condition),width = .4, size=.5,position = position_dodge(width = .9))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,75))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}  
figure2A2<-PlotInCFUs2()
figure2A2

#With the mutants

#####
#Figure 2B
#####
#this is taken from AggregateCounts.Rmd section Plot Aggregagte size bins

PlotHistSumFinal<-function(rep.df,cond.df,region.df, y_var, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .5,position = position_dodge(width = .75) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

#only difference between these two should be "scale_color_grey"
PlotHistSumFinalStrains<-function(rep.df,cond.df,region.df, y_var, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 1),size=2)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=5, position = position_dodge(width = 1) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}#only difference between these two should be "scale_color_grey
PlotHistSumFinalStrains(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency","Strain")

@@

PlotAbData3<-function(df,xaxis,yaxis, error, fill){
ggplot()+
  geom_col(data = df %>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],y=.data[[yaxis]], fill = .data[[fill]]),size=3,position = position_dodge( width = .9))+
  geom_errorbar(data = df%>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],ymin=(.data[[yaxis]]-.data[[error]]), ymax = (.data[[yaxis]]+.data[[error]]), group = .data[[fill]]),
                width = 0, size=.5,position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #scale_y_log10(expand = expand_scale(mult = c(0, 0)))+
  #facet_grid(.~Species)+
  scale_fill_grey(labels = c("Mono-culture","Co-culture wt", "Co-culture pqsL"))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
  labs(x = "", y = "Survival fraction Structured/Unstructured")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotAbData3(AbDataUnstructureStats,"Species","MeanRatio","SESurvival", "Condition")
PlotAbData3(AbDataUnstructureStats,"Species","MeanDifference","SEDifference", "Condition")
#now using the jittel points

>>>>

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library(stringr)

@@

@@

PlotInCFUs2<- function(){
  ggplot()+
    geom_jitter(data = CFUInOutPostWt,aes(x=Species,y=PercentIn, color = Condition),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent), ymax = (meanInPercent), group = Condition),width = .4, size=.5,position = position_dodge(width = .9))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,75))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}  
figure2A2<-PlotInCFUs2()
figure2A2
#####
#Figure 2B
#####
#this is taken from AggregateCounts.Rmd section Plot Aggregagte size bins

PlotHistSumFinal<-function(rep.df,cond.df,region.df, y_var, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .5,position = position_dodge(width = .75) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

PlotHistSum(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency","Strain")

@@

PlotAbData3<-function(df,xaxis,yaxis, error, fill){
ggplot()+
  geom_col(data = df %>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],y=.data[[yaxis]], fill = .data[[fill]]),size=3,position = position_dodge( width = .9))+
  geom_errorbar(data = df%>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],ymin=(.data[[yaxis]]-.data[[error]]), ymax = (.data[[yaxis]]+.data[[error]]), group = .data[[fill]]),
                width = 0, size=.5,position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #scale_y_log10(expand = expand_scale(mult = c(0, 0)))+
  #facet_grid(.~Species)+
  scale_fill_grey(labels = c("Mono-culture","Co-culture wt", "Co-culture pqsL"))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
  labs(x = "", y = "Survival fraction Structured/Unstructured")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotAbData3(AbDataUnstructureStats,"Species","MeanRatio","SESurvival", "Condition")
PlotAbData3(AbDataUnstructureStats,"Species","MeanDifference","SEDifference", "Condition")
#now using the jitter points
